Towards practical dynamic induction control of wind farms: analysis of optimally controlled wind-farm boundary layers and sinusoidal induction control of first-row turbines

### 2018-02-06 draft.tex
Comments JM: abstract

\begin{abstract}
	Wake interactions between wind turbines in wind farms entail reduced energy extraction in downstream rows, inciting research into coordinated wind-farm control strategies for optimal power extraction. In recent work, optimization and large-eddy simulation were combined to study optimal dynamic induction control of wind farms with power gains up to 20\% (Munters \& Meyers 2017 \emph{Phil Trans R Soc A} \textbf{375}, 20160100, doi:10.1098/rsta.2016.0100). However, computational costs associated with the optimal control simulations impede practical implementation of this work. Furthermore, the resulting optimal control signals are tuned to specific flow events and hence cannot be used in practice, and the complexity of these signals complicated the derivation of simplified control strategies. The current work focuses on further analysis of the optimization results of Munters \& Meyers. The analysis shows that wind-farm controls are optimized in a uni-directional manner with little upstream propagation of information, and that turbines can be classified into first-row, intermediate-row, and last-row turbines based on their optimal control dynamics. Although the control mechanisms for intermediate-row turbines remain unclear based on the current analysis, for first-row turbines it is found that the optimal controls increase wake mixing through periodically shed vortex rings. This behavior is mimicked with a simple sinusoidal thrust control strategy for first-row turbines, resulting in robust power gains for turbines in the entrance region of the farm.
\end{abstract}

>>>>

\begin{abstract}
	Wake interactions between wind turbines in wind farms lead to reduced energy extraction in downstream rows. In recent work, optimization and large-eddy simulation were combined with optimal dynamic induction control of wind farms to study the mitigation of these effects, showing potential power gains up to 20\% (Munters \& Meyers 2017 \emph{Phil Trans R Soc A} \textbf{375}, 20160100, doi:10.1098/rsta.2016.0100). However, the computational cost associated with the optimal control simulations impedes practical implementation of this approach. Furthermore, the resulting control signals optimally react to the specific instantaneous turbulent flow realizations in the simulations, so that they cannot be simply be used in general. The current work focuses on the detailed analysis of the optimization results of Munters \& Meyers, with the aim to identify simplified control strategies that mimic the optimal control results and can be used in practice. The analysis shows that wind-farm controls are optimized in a parabolic manner with little upstream propagation of information. Moreover, turbines can be classified into first-row, intermediate-row, and last-row turbines based on their optimal control dynamics. At the moment, the control mechanisms for intermediate-row turbines remain unclear, but for first-row turbines we find that the optimal controls increase wake mixing by periodic shedding of vortex rings. This behavior can be mimicked with a simple sinusoidal thrust control strategy for first-row turbines, resulting in robust power gains for turbines in the entrance region of the farm.
\end{abstract}
